---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# group.unique

<!-- badges: start -->
<!-- badges: end -->

The goal of group.unique is to count the unique (aka distinct) values of a variable that exist in each group of another variable of a dataset. It will produce a tibble with two columns. The first is the grouped values, and the second is the number of unique values per group.

## Installation

You can install the development version of group.unique from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-jg1121")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(datateachr) #loading in example datasets
library(group.unique) #loading in the package
group.unique(vancouver_trees, neighbourhood_name, common_name)
```

