---
title: "Assignment-B1"
author: "Jennifer Green"
date: "2022-10-31"
output: github_document
---
In this assignment we will be making a function in R, documenting it, and testing it.

##Setup
```{r message= FALSE}
#Loading the needed packages 
library(tidyverse)
library(testthat)
library(roxygen2)
library(gapminder)
library(ggplot2)
library(datateachr)
library(palmerpenguins)
library(devtools)
```

##Exercise 1 & 2 - Make a function & Document the function

I used the code sequence featured below multiple times in my STAT545A milestone to compute the number of observations for a variable. So, I wanted to make a function out of it. The code does the following with the input of a data table:

1) Groups by a column variable
2) Summarizes the groups by the number of distinct observations of another variable.

Here I will be creating and documenting the function to count the unique values by group
```{r}
# Documentation of function

#' Count the unique values of a variable per a grouped variable.
#'
#' This function counts the unique (aka distinct) values of a variable that exist in each group of another variable of a dataset. It will produce a tibble with two columns. The first is the grouped values, and the second is the number of unique values per group. 
#' 
#'
#' @param dataset The dataset containing the variables that you wish to count unique values of a group from 
#' @param grouped_variable Name of the column containing the variable that you want to group.
#' @param unique_variable Name of the column containing the variable that you want to extract the number of unique/distinct values from for each group in the grouped_variable.
#'
#' @return A tibble with two columns. The first column is the grouped values with the column name of the grouped_variable. The second column is the number of unique values of the other variable (unique_variable) per each group, with the column name "count_of_unique". 


# Creating my function
Group_unique <- function(dataset, grouped_variable, unique_variable) {
  dataset %>% group_by({{grouped_variable}}) %>% 
  summarize(unique_variable_count = n_distinct({{unique_variable}}))
}
```

##Exercise 3- Examples!
Here I will look at 3 different datasets and summarize a grouped variable by a distinct value of another variable. This can help us answer specific questions about the dataset. 

###Example: How many different types of trees are there in each neighbourhood of Vancouver?

Here I will count the number of different tree species (common_name) in each neighbourhood ("neighbourhood_name") of Vancouver, BC, using the *vancouver_trees* dataset

```{r}
Group_unique(vancouver_trees, neighbourhood_name, common_name)
```
This gives us an idea of the biodiversity per neighborhood! We could later sort the count_of_unique column to know which neighbourhoods have the most biodiversity. 

###Example: How many different penguin species are there on each island?

Here I will count the number of different penguin species ("species") on each island ("island") sampled in the *penguins* dataset. 

```{r}
Group_unique(penguins, island, species)
```
Here we can learn that 2 of the islands only had 2 out of the 3 species studied. The other island only had one of the three species. 

###Example: How many different countrys were sampled per year in gapminder?

Here I will count the number of different countries ("country") investigated per year ("year") in the using the *gapminder* dataset. This could help us know if the dataset was skewed or bias.

```{r}
Group_unique(gapminder, year, country)
```
It looks like they surveyed the same number of countries (142) every year. These were likely the same countries each year. 

##Exercise 4: Test the Function
```{r}
#is tibble

#check that count of unique adds up to total nrows of the unique variable

#expect error when variable name isnt in given dataframe

test_that("Name of Test",
          {expect_true(is_tibble(Group_unique(vancouver_trees, 
                                      on_street,
                                      genus_name))) #Test that the final output is a tibble object
            expect_error(Group_unique(vancouver_trees,
                                      fake_x,
                                      fake_y)) #There should be an error when variable name isn't in dataset
            expect_identical((Group_unique(vancouver_trees, 
                                           on_street, 
                                           genus_name)), 
                              (vancouver_trees %>% 
                                 group_by(on_street) %>% 
                                 summarize(unique_variable_count = 
                                             n_distinct(genus_name)))) #Test that the function gives an identical output to doing the problem manually
            
}
          )
```
